Democratizing Secure Two-Party Computation

### 2017-10-13 OaklandSubmission/intro.tex
intro related

\textbf{Programmability.} \tool is a programmer-friendly framework to express the function to be computed and uses a mix of arithmetic and boolean SMC back-ends. We illustrate the above toy example of $w^Tx >b$ in our language in \figureref{ex-sml}. As is clear from the code, the programmer is not required to write keywords such as {\em secret} or {\em public} and can remain completely oblivious of the cryptographic back-end. In contrast, \figureref{ex-aby} illustrates the same example using the framework in ABY \cite{aby}. Here, as already mentioned, the programmer needs to write the low level gates like $\mathrm{MULT, ADD, CONS, GT}$, etc. The programmer is also required to use the appropriate share conversion gates such as A2Y that converts Arithmetic shares to Yao shares.

@@

\noindent\textbf{Related Work} \divya{I think we should say a few words here about the following: minionn, verilog paper, tasty, 
\cite{lambdaps,wysteria}

}

\newpage

>>>>

\textbf{Programmability.} \tool is a programmer-friendly framework to express the function to be computed and uses a mix of arithmetic and boolean SMC back-ends. We illustrate the above toy example of $w^Tx >b$ in our language in \figureref{ex-sml}. As is clear from the code, the programmer is not required to write keywords such as {\em secret} or {\em public} and can remain completely oblivious of the cryptographic back-end. In contrast, \figureref{ex-aby} illustrates the same example using the framework in ABY \cite{aby}. Here, as already mentioned, the programmer needs to write the low level gates like {\tt MULT, ADD, CONS, GT}, etc. The programmer is also required to use the appropriate share conversion gates such as {\tt A2Y} that converts Arithmetic shares to Yao shares. Moreover, it is easy to maintain code in \tool and small change to the functionality requires only a small change in the code. In contrast, working with ABY, even for a small change a developer might have to re-work the whole circuit for efficiency reasons. We describe these examples in detail in \sectionref{ex}.

@@

\noindent\textbf{Other Related Work} 
Before ABY \cite{aby}, to improve efficiency, several works proposed
to mix secure computation protocols based on homomorphic
encryption with Yao’s garbled circuits protocol, e.g., \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,shropfer11}
  and developed tools that allowed writing a mixed SMC protocol, e.g., \cite{bogdanov,lone,tasty}. The assignment can
even be done automatically as was shown in \cite{autoS}. 
However, as noted by ABY, due to high conversion cost between homomorphic encryption and Yao's garbled circuit, these mixed protocols do not gain much over single protocol. Also, none of these works give a high-level developer-friendly language support.
No prior work has given a formal type system and operational semantics for mixed arithmetic and boolean back-ends.
In our evaluation, we use benchmarks for the problem of secure prediction where the cloud holds the secret model and the client holds the secret input. For this problem various works have considered tailor-made protocols depending on the model considered \cite{shafindss,wu,secureml,minionn}. In our evaluation, we compare our performance with these specialized protocols and give competitive run-times. We provide a detailed survey of related work in \sectionref{related}.
